\documentclass[11pt]{article}

\title{Numerical stability of motion estimation in fMRI time series}

\author{Tristan Glatard, Pierre Bellec}

\begin{document}

\maketitle

\section{Introduction}

Micro-movements Power. Review paper Power.

Bootstrap is promising but fixing the algorithms would be better.

% Reproducibility, including OS

% Replicability


\section{Methods}

% Dataset and one-voxel perturbation
We randomly selected 680 datasets from 34 sites of the CoRR dataset, 
corresponding to 543 subjects with $TR \in [0.645s, 3.0s]$ and number 
of volumes in $[120, 899]$. On each dataset, we applied a one-voxel 
perturbation similar to~\cite{lindsay}: we randomly selected a non-zero 
voxel in a 30-mm box centered at the center of the image, and we 
increased its intensity by 1\%, rounded to the nearest integer as the 
datasets were encoded as unsigned integers.

% Motion estimation methods + bootstrap.
We estimated the motion parameters at each volume of the initial and 
perturbated datasets using (1) FSL \texttt{mcflirt} 5.0.6, (2) SPM12 
\texttt{spm\_realign}, (3) AFNI \texttt{3dvolreg} 18.1.26 and (4) NIAK 
cog. to the initial and perturbated datasets. All methods were 
configured to estimate the 6 motion parameters with respect to the 
first volume in the dataset. We also computed a bootstraped version of 
Niak and FSL, in which we executed 30 repetitions of the initial method 
after having applied an extra one-voxel perturbation in addition to the 
initial one. The bootstrap result was computed as the average 
transformation from the 30 samples, that is, from the averages of the 6 
parameters of the 30 transformations.

For each dataset, we calculated the frame displacement (FD) measure 
proposed by~\cite{power2012spurious} on $T_1oT_2^{-1}$, where $T_1$ and $T_2$ were 
the transformations independently estimated on the initial and 
perturbated datasets.



% FD of T1oT2-1, Dice of scrubbed volumes

\section{Results}

% Correlations between FD values

% Effect of perturbation by algorithm (FD, Dice of scrubbed volumes)

% Effect of perturbation by site (FD, Dice of scrubbed volumes)

% Effect of perturbation by TR value (FD, Dice of scrubbed volumes)

% Distribution of bootstrap estimates

\section{Discussion}

Accuracy needs to be discussed.


\end{document}
